\documentclass[master=ewit]{kulemt}
\setup{title={Newton-type operator splitting methods for embedded model predictive control},
  author={Willem Melis},
  promotor={Prof.\,dr.\,ir.\ Panagiotis Patrinos},
  assessor={Prof.\,dr.\,ir.\ Johan Suykens \\ Prof.\,dr.\,ir.\ Daan Huybrechs},
  assistant={dr.\,Pantelis Sopasakis}}
% The following \setup may be removed entirely if no filing card is wanted
\setup{filingcard,
  translatedtitle=,
  udc=621.3,
  shortabstract={TODO: Add the same abstract here, containing no more than 500
    words. \LaTeX\ commands can be used here. Blank lines (or the command
    \texttt{\string\pa r}) are not allowed!
    \endgraf endgraf}}
% Uncomment the next line for generating the cover page
% \setup{coverpageonly}

\setup{filingcard, % Do not change anything in this line!
	%
	% Give the dutch translation of the title of your master's thesis below between the { and }:
	translatedtitle={Newton-type operator splitsen methoden voor embedded model predictive control},
	%
	% UDC number depends on your discipline. see http://www.udcsummary.info/php/index.php to find the number.
	udc=621.3,
	%
	% Add between { and } a short abstract.
	% Empty lines or the commando \par are not admitted.
	% Be careful with special TeX-signs #$%&^_~{}\ !!
	shortabstract={%
    The goal of this thesis is to implement a Matlab and Python library that generates a MPC controller in C that makes use of the PANOC algorithm. No toolboxes or external libraries were used to generated the C code, with the  exception of Casadi. Casadi is used to generate the gradient used in the proximal gradient algorithm. In the first chapters the PANOC algorithm is discussed. Followed by a high level view of nmpc-codegen, the software package constructed with this thesis. After the theory some simulation results are included that compare PANOC to some of the state of the art interior point and SQP solvers. PANOC dominates the simulations when the system equations are small, but loses this advantage when complex system equations are used. It does however always use less memory then the alternatives. The final chapter discuses a recent improvement of the PANOC algorithm. When adding soft constraints onto the problem, the weights of theses constraints must be set. Setting the weights too low will result in violations of those constraints, and setting it too worsens the condition of the problem. Recent research surrounding PANOC and the augmented Lagrangian sudgest that by defining and solving the MPC problem iteratively, the performance can be significantly improved. It is also much more intuitive to tune the augmented Lagrangian then to tune the weights of the constraints.	
}}

% Choose the main text font (e.g., Latin Modern)
\setup{font=lm}

\bibliographystyle{IEEEtran}

\usepackage{algorithm} 
\usepackage{algcompatible}
\usepackage{algpseudocode}
%\usepackage[parfill]{parskip} % paragraphs are seperated with an enter space

% Finally the hyperref package is used for pdf files.
% This can be commented out for printed versions.
\usepackage[pdfusetitle,colorlinks,plainpages=false]{hyperref}

\usepackage{graphicx}
\graphicspath{{./figs/}}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{tabularx}

% package used to import poster
\usepackage[final]{pdfpages}

\usepackage{amsmath,amsthm,amssymb}
\DeclareMathOperator{\project}{project}
\DeclareMathOperator{\prox}{prox}
\DeclareMathOperator{\boxfunction}{box}
\DeclareMathOperator{\argmax}{argmax}
\DeclareMathOperator*{\minimize}{minimize}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\other}{other}

\newcommand{\Lagr}{\mathcal{L}} % this uses the amssym package

%\includeonly{chap-n}
\begin{document}

\begin{preface}
I would like to thank everyone that contributed in any way to this thesis, especially my promoter P. Patrinos and mentor P. Sopasakis. I would also like to thank the jury for reading the text. Finally i would like to thank my family for the moral support they gave me this last year.
\end{preface}

\tableofcontents*

\include{./extra/abstract}

% A list of figures and tables is optional
\listoffigures
\listoftables
% If you only have a few figures and tables you can use the following instead

% The list of symbols is also optional.
% This list must be created manually, e.g., as follows:
\include{./extra/symbols_abbreviations}

% Now comes the main text
\mainmatter

%\include{./extra/intro}
\include{./chapters/MPC}
\include{./chapters/part2_prox_gradient}
\include{./chapters/part3_PANOC}
\include{./chapters/part4_LBFGS}
\include{./chapters/part5}
\include{./chapters/part6}
\include{./chapters/part7}
\include{./chapters/part8_extra_accel_LA}
\include{./extra/conclusion}

% If you have appendices:
\appendixpage*          % if wanted
\appendix
\include{./appendix/appendix}

\backmatter
% The bibliography comes after the appendices.
% You can replace the standard "abbrv" bibliography style by another one.
\bibliographystyle{abbrv}
\bibliography{references}

\end{document}